Do we need detailed demographic data to forecast plant population responses to climate change?

### 2016-07-01 manuscript/manuscript.Rmd
adds Britta comments; sent to MBH and PBA

Perhaps the greatest challenge for ecology in the 21st century is to forecast the impacts of environmental change [@Clark2001; @Petchey2015]. Forecasts require sophisticated modeling approaches that fully account for uncertainty and variability in both ecological process and model parameters [@Luo2011a; but see @Perretti2013a]. The increasing statistical sophistication of population models [@Rees2009] makes them promising tools for predicting the impacts of environmental change on species persistence and abundance. But reconciling the scales at which population models are parameterized and the scales at which environmental changes play out remains a challenge [@Clark2010; @Freckleton2011; @Queenborough2011; @Clark2012]. Most population models are built using demographic data from a single study site because tracking the fates of individuals is so difficult. The resulting models cannot be applied to the landscape and regional scales relevant to decision-making without information about how the estimated parameters respond to spatial variation in biotic and abiotic drivers [@Sæther2007]. The limited spatial extent of individual-level demographic datasets constrains our ability to use population models to address applied questions about the consequences of climate change.

Aggregate measures of population status, rather than individual performance, offer an intriguing alternative for modeling populations [@Clark2004; @Freckleton2011]. Population-level data cannot provide inference about demographic mechanisms, but might be sufficient for modeling future population states, especially because such data are feasible to collect across broad spatial extents [e.g., @Queenborough2011]. The choice between individual and population-level data involves a difficult trade-off: while individual-level data are necessary for mechanistic models, population-level data enable models that can be applied over greater spatial and temporal extents. An open question is how much forecasting skill is lost when we build models based on population rather than individual-level data.

@@

In the above, $w_{i,t}$ is the crowding that genet _i_ in year _t_ experiences from conspecific neighbors in quadrat *q*. The spatial scale over which conspecific neighbors exert influence on any genet is determined by $\delta$. The function is applied for all _k_ conspecific genets that neighbor the focal genet at time _t_, and $d_{ik,q,t}$ is the distance between genet _i_ and conspecific genet _k_ in quadrat *q*. We use regression-specific (survival and growth) $\delta$ values estimated by @Chu2015.

>>>>

Perhaps the greatest challenge for ecology in the 21st century is to forecast the impacts of environmental change [@Clark2001; @Petchey2015]. Forecasts require sophisticated modeling approaches that fully account for uncertainty and variability in both ecological process and model parameters [@Luo2011a; but see @Perretti2013a]. The increasing statistical sophistication of population models [@Rees2009] makes them promising tools for predicting the impacts of environmental change on species persistence and abundance. But reconciling the scales at which population models are parameterized with the scales at which environmental changes play out remains a challenge [@Clark2010; @Freckleton2011; @Queenborough2011; @Clark2012]. Most population models are built using demographic data from a single study site because tracking the fates of individuals is so difficult. The resulting models cannot be applied to the landscape and regional scales relevant to decision-making without information about how the estimated parameters respond to spatial variation in biotic and abiotic drivers [@Sæther2007]. The limited spatial extent of individual-level demographic datasets constrains our ability to use population models to address applied questions about the consequences of climate change.

Aggregate measures of population status, rather than individual performance, offer an intriguing alternative for modeling populations [@Clark2004; @Freckleton2011]. Population-level data cannot provide inference about demographic mechanisms, but might be sufficient for modeling future population states, especially because population-level data, such as plant percent cover, are feasible to collect across broad spatial extents [e.g., @Queenborough2011]. The choice between individual and population-level data involves a difficult trade-off: while individual-level data are necessary for mechanistic models, population-level data enable models that can be applied over greater spatial and temporal extents. An open question is how much forecasting skill is lost when we build models based on population rather than individual-level data.

@@

In equation 3, $w_{i,t}$ is the crowding that genet _i_ in year _t_ experiences from conspecific neighbors in quadrat *q*. The spatial scale over which conspecific neighbors exert influence on any genet is determined by $\delta$. The function is applied for all _k_ conspecific genets that neighbor the focal genet at time _t_, and $d_{ik,q,t}$ is the distance between genet _i_ and conspecific genet _k_ in quadrat *q*. We use regression-specific (survival and growth) $\delta$ values estimated by @Chu2015.
